# Courses

## Compulsory courses

### Designing a PhD Project 2021-2022

The aim of this course is to help doctoral students develop a research plan for their doctoral project.

Assignment 1: Discussion of final research plans

Assignment 2: Discussion of dissertations

### Foundations of Economic History

Foundations of Economic history is a course that will run for the entire academic year 2021-2022.

Assignment 1: Growth and stagnation in the pre-industrial society.

### Archives, Primary Sources, Dataset

Full course code and title: EKHT34 - Economic History: Advanced Topics in Economic History - Research in Economic History: Archives, Primary Sources, Dataset.

Convened by Jaco Zuijderduijn, this course looks at primary sources: how to find thm, why they were compiled, what they can tell us.

#### Idea for this course.

Taxation in Sweden evolved from an origin of revenue excised based on the size of the farm inhabited by a family, where one *mantal* was a farm large enough to sustain one family, hence the name [*mantalspenningar*](https://www.familysearch.org/wiki/en/Swedish_Mantalsl%C3%A4ngd), a tax levied on every person aged 15 to 63. 

...

The Mantals och skattskrifningslängd records:

```{r}
library(tidyverse)
tibble(headings = c("Qvarterets namn, fasighetens beskaffenhet samt dervarande verk och inrättningar; de inom egendomen boende personers namn, titel, embete eller befattning, yrke eller näringsfang; äfvensom andra antechningar för mantalskrifningen",
                    "Mantalsuppgiftens nummer",
                    "Antal personer, som böra erlägga mantals-penningar (M/K)"),
       eng_headings = c("The name of the neighborhood, the nature of the facility and the works and establishments there; the name, title, office or position, occupation or occupation of the persons residing in the property; as well as other notes for the mantal writing",
                        "Mantal information number",
                        "Number of people who should pay mantal money (M/W)"))
```


### Designing a PhD Project 2021-2022

## Elective courses

## Additional courses (not for credit)

### Econ 2355: Unleashing novel data at scale

The Harvard course taught by Melissa Dell called [Economics 2355: Unleashing novel data at scale](https://dell-research-harvard.github.io/teaching/economics-2355) is intended to be a primer on using Melissa Dell's python tool called [Layout Parser](https://layout-parser.github.io/). The tool lowers the cost of digitizing historical sources using deep learning techniques. 

The course covers why it might be useful to invest time in digitizing historical sources, how to do so in the most efficient manner, and how to analyze the resulting data using cutting-edge natural language processing (NLP).

The course is offered on a [Youtube channel](https://www.youtube.com/watch?v=9fAjz0d2G4U&list=PLGTgQIsun7udZFo20jeJ4gq-T8Sq6b5bU&ab_channel=MelissaDell) in addition to a knowledgebase (set of lecture notes and refernces), linked [here](https://dell-research-harvard.github.io/teaching/economics-2355).

<iframe width="560" height="315" src="https://www.youtube.com/embed/9fAjz0d2G4U" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

Progress: on lecture 8 of 20, pretty useful in conjunction with learning how Layout Parser works.

### Coursera's deep learning specialization

This is a course taught by deep learning legend Andrew Ng who is also the founder of Coursera. It is an introduction to the programming language python and deep learning neural network architectures like CNNS, the building block of image processing used in Layout Parser.

Progress: week 3, it's pretty tough as I haven't much experience in python.

### Mastering Shiny

Mastering Shiny is a textbook by Hadley Wickham that teaches you how to build interactive applications, reports and websites. It is super fun, and can be useful to convey research to a general audience and be presented alongside a research paper. The book is presented in 3 sections.

```{r}
knitr::include_graphics("https://mastering-shiny.org/")
```

There is an interesting example of this style of interactive visualisation in companion to a research write up for a [recent paper](https://blueprintlabs.mit.edu/research/using-admissions-lotteries-to-validate-and-improve-school-quality-measures/) on measuring school quality in New York City:

```{r}
knitr::include_url("https://public.tableau.com/shared/9R9MBP4C8?:display_count=y&:origin=viz_share_link&:embed=y")
```

Progress: in the second section, `shiny in action`.
